Report

### 2020-10-06 report.Rmd
Add nbnode + standardized richness

```{r p-bivar, cache = TRUE, fig.cap = bivar_cap, fig.height = 10}
cowplot::plot_grid(
  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:4], ncol = 2),
  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[1:4], ncol = 2),
  ncol = 1, 
  axis = "rlbt",
  align = "hv",
  label_y = 1.01,
  label_x = .40,
  labels = c("Little community", "Big community")
)

cowplot::plot_grid(
  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[5:8], ncol = 2),
  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[5:8], ncol = 2),
  ncol = 1, 
  axis = "rlbt",
  align = "hv",
  label_y = 1.01,
  label_x = .40,
  labels = c("Little community", "Big community")
)
```

- Intercept close to 0 for all but richness in big communities 
- Same slope between big and little communities except for connectance

@@

##

```{r, eval = FALSE}
slope_com_net <- temporal_dynamics_coef %>%
  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
  select(station, coeff, estimate) %>%
  pivot_wider(names_from = "coeff", values_from = estimate)

absolute_slope_biomass <- temporal_dynamics_coef %>%
  filter(coeff %in% get_biomass_var(), term == "slope") %>%
  select(station, coeff, estimate) %>%
  mutate(
    absolute_slope =  abs(estimate),
    trend_sign = if_else(estimate > 0, "positive", "negative")
  ) %>%
  left_join(slope_com_net, by = "station")

metrics <- unique(temporal_dynamics_coef$coeff)[!unique(temporal_dynamics_coef$coeff) %in% get_biomass_var()]

p <- vector("list", length = length(metrics))
for (i in seq_along(metrics)) {
  p[[i]] <- 
    absolute_slope_biomass %>%
    ggplot(aes_string(x = "absolute_slope", y = metrics[i])) +
    geom_point(aes(color = trend_sign)) +
    facet_wrap(facets = ~ coeff, scales = "free") +
    labs(title = metrics[i])
}
p
```

@@

```{r p-tmp-dyn, cache = TRUE}

@@

```{r, fig.height = 45}
st_decrease_increase_rigal <- biomass_classif_rigal %>%
  filter(variable == "log_bm_std") %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))
data_decrease_increase <- full_data2 %>%
  filter(station %in% st_decrease_increase_rigal$station)

@@

```{r, fig.height = 45}
st_decrease_increase_rigal_biomass <- rigal_classification %>%
  filter(variable == "bm_std") %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

@@

@@

model_bm_vif %>%
  ggplot(aes(y = vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free_x")
```

```{r}
bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
```

```{r, eval = TRUE}
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]

```{r}
filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]

```{r}
filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]

```{r}
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
```

```{r}
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]

```{r, eval = FALSE}
library(segmented)

mod_tlvl <- lm(estimate ~ linear_slope, model_int$data[[2]])
mod_tlvl <- lm(
  estimate ~ linear_slope*decreasing*group,#(linear_slope < 0)*linear_slope + (linear_slope >= 0)*linear_slope,
  mutate(model_int$data[[2]], decreasing = linear_slope < 0)
)
seg_tlvl <- segmented(mod_tlvl, seg.Z=~linear_slope)
plot(seg_tlvl)

mod_richness <- lm(estimate ~ linear_slope, model_int$data[[2]])
test <- segmented(mod_richness, seg.Z=~linear_slope)
plot(test)

car::vif(test)
```

@@

```{r}

@@

sax_all_variable %>%
  filter(
    station %in% cba_rigal_sax$station,
    !variable %in% c("biomass", "nbnode")
    ) %>%
  ggplot(aes(x = sax)) +
  geom_bar() +
  facet_wrap(facets = ~variable)

>>>>

@@

model_bm_vif %>%
  ggplot(aes(y = vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

```{r}
loadd(bm_net_group)
bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
```

```{r, eval = FALSE}
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]

```{r, eval = FALSE}
filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]

```{r}
loadd(log_bm_net_group)
```

```{r, eval = FALSE}
filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]
filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]

```{r, eval = FALSE}
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
```

```{r, eval = FALSE}
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]

@@

```{r p-tmp-dyn, cache = TRUE, eval = FALSE}

@@

```{r, cache = TRUE, fig.height = 45}
st_decrease_increase_rigal <- biomass_classif_rigal %>%
  filter(variable == "log_bm_std") %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))
data_decrease_increase <- full_data2 %>%
  filter(station %in% st_decrease_increase_rigal$station)

@@

```{r, cache = TRUE, fig.height = 45}
st_decrease_increase_rigal_biomass <- rigal_classification %>%
  filter(variable == "bm_std") %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

@@

### Richness

```{r, cache = TRUE, fig.height = 45}
var_tmp <- "rich_std"
st_decrease_increase_rigal <- rigal_classification %>%
  filter(variable == var_tmp) %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

### Number of nodes

```{r, cache = TRUE, fig.height = 45}
var_tmp <- "nbnode_std"
st_decrease_increase_rigal <- rigal_classification %>%
  filter(variable == var_tmp) %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

@@

@@

@@

sax_all_variable %>%
  filter(
    station %in% cba_rigal_sax$station,
    !variable %in% c("biomass", "nbnode")
    ) %>%
  ggplot(aes(x = sax)) +
  geom_bar() +
  facet_wrap(facets = ~variable)
```
